---
title: "`html_clean` template example"
output:
  rmdformats::html_clean:
    fig_width: 6
    self_contained: false
    fig_height: 6
    highlight: tango
    thumbnails: true
    lightbox: true
    gallery: true
    toc_depth: 3
---


```{r knitr_init, echo=FALSE, results="asis", cache=FALSE}

## Global options
options(max.print = "75")
knitr::opts_chunk$set(echo = FALSE,
	             cache = FALSE,
               prompt = FALSE,
               tidy = FALSE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
knitr::opts_knit$set(width = 75)
```

```{r}
library(knitr)
library(rmdformats)
```

# Code and tables

## Syntax highlighting

Here is a sample code chunk, just to show that syntax highlighting works as expected.

```{r sh, echo=TRUE, eval=TRUE}
library(ggplot2)
library(dplyr)

not_null <- function (v) {
  if (!is.null(v)) return(paste(v, "not null"))
}

data(iris)
tab <- iris %>%
  group_by(Species) %>%
  summarise(Sepal.Length = mean(Sepal.Length),
            Sepal.Width  = mean(Sepal.Width),
            Petal.Length = mean(Petal.Length),
            Petal.Width  = mean(Petal.Length))
```


## Verbatim

Here is the structure of the `iris` dataset.

```{r iris_str, echo=TRUE}
str(iris)
```

## Table

Here is a sample table output.

```{r iris_table}

kable(tab)

```

Here we display a crosstab displayed in several different ways with a "pills"
interface. To do this, just pass your `table()` result to the `pilltabs()`
function.

```{r iris_pilltabs, results="asis"}

iris$seplc <- cut(iris$Sepal.Length,3)
tab <- table(iris$Species, iris$seplc)
pilltabs(tab)

```



# Dynamic toc with for loop

We present different themes for `ggplot` here with a `for` loop.

Click an image to navigate between themes.

```{r , results = 'asis', echo = TRUE}
library(ggplot2)
library(ggthemes)
library(hrbrthemes)

ggplot_themes <- list("Black and white"   = theme_bw(), 
                      "Classic"           = theme_classic(), 
                      "Dark"              = theme_dark(), 
                      "Minimal"           = theme_minimal(),
                      "Map"               = theme_map(),
                      "Light"             = theme_light(),
                      "Void"              = theme_void())

ggthemes <- list("Calc"                   = theme_calc(),
                 "Economist"              = theme_economist(),
                 "Economist white"        = theme_economist_white(),
                 "Excel"                  = theme_excel(),
                 "Few"                    = theme_few(),
                 "Five Thirty Eight"      = theme_fivethirtyeight(),
                 "G. Docs"                = theme_gdocs(),
                 "High Chart"             = theme_hc(),
                 "Inverse gray"           = theme_igray(),
                 "Linedraw"               = theme_linedraw(),
                 "Pander"                 = theme_pander(),
                 "Solarized"              = theme_solarized(),
                 "Solarized 2"            = theme_solarized_2(),
                 "Solid"                  = theme_solid(),
                 "Stata"                  = theme_stata(),
                 "Tufte"                  = theme_tufte(),
                 "Wall Street Journal"    = theme_wsj())

hrbrthemes <- list("Ipsum (Arial Narrow)" = theme_ipsum())

themes <- list("ggplot2"    = ggplot_themes, 
               "ggthemes"   = ggthemes,
               "hrbrthemes" = hrbrthemes)

for (j in seq_along(themes)){
  cat(paste0('\n\n## ', names(themes[j]), ' themes \n\n'))
  for (i in seq_along(themes[[j]])){
    cat(paste0('\n\n### ', names(themes[[j]][i]), '\n\n'))
    print(ggplot(data=iris) + 
            geom_point(aes(x=Petal.Width, y=Petal.Length, color=Species)) + 
            themes[[j]][i] + 
      ggtitle(names(themes[[j]][i])))
  }
}
```

